Report

### 2022-06-27 manuscript.Rmd

### using bain objects
The `pbf()` function also works when objects are first converted to `bain` objects. In this specific example, each `bain` object corresponding to one of the three samples has the $H_0$ and $H_A$ in common, but contains one sample-specific hypothesis. The `pbf()` function only returns output for the hypotheses that are present in all results. When `bain` objects are passed to the `pbf()`, no additional hypotheses need to be passed to `pbf()` as they are already saved in the objects.

@@

As can be seen, the results are identical to the results in the previous example. This means that the sample-specific hypotheses have been left out and only the hypotheses that each sample has in common are retained.

When there is no hypothesis that is shared by each sample, `pbf()` throws an error.
```{r}
bains_different_hyps <- list(
  bain(lm_sample1, "site2=site1=site3=site4=site5"),
  bain(lm_sample2, "site2=site1=site3>site4=site5"),
  bain(lm_sample3, "site2&site3>site1&site4&site5")
)

@@

```
The function returns an error stating that the samples have no hypothesis in common and thus the PBF cannot be calculated.

### using named vectors
Another specific use-case is when the raw data from different samples is not available. In this case, the researcher only has access to the parameter-values that are provided in the research papers. Because the `pbf()` function inherently converts objects to `bain` objects, each sample requires three pieces of information in order to be usable: the named parameter estimates, a covariance matrix of their standard errors and the sample size. First these values are extracted from all samples. A function is created that extracts is information which is then used to extract the necessary information from all samples.

```{r}
get_estimates <- function(sample){
  number_sites <- length(levels(sesamesim$site))

@@

And finally, on these objects, `pbf()` can be called.
```{r}
pbf(bain_allsamples_ests)
```
<!-- It is interesting that these estimates are not identical to the other examples... Is that because we do not have ALL information available in this use-case, or is something off in the script? -->

>>>>

### using bain objects

The `pbf()` function also accepts multiple `bain` objects.
This makes it possible to, for example, evaluate different sets of hypotheses for multiple data sets before using the resulting `bain` objects to aggregate the evidence for all hypotheses those datasets share in common.
The example below illustrates this princuple.
Each analysis has two hypotheses in common, but also contains one sample-specific hypothesis.
The `pbf()` function is called on the resulting `bain` object and returns output for the two common hypotheses.
Note that, in this case, `pbf()` does not require an argument `hypotheses`, as the hypotheses are contained in the `bain` objects.

@@

As can be seen, the results are identical to the results in the previous example. This means that the sample-specific hypotheses have been left out and only the hypotheses that each sample has in common are retained.
When there are no common hypotheses, `pbf()` throws an error.

```{r, echo = FALSE, eval = FALSE}
bains_different_hyps <- list(
  bain(lm_sample1, "site2=site1=site3=site4=site5"),
  bain(lm_sample2, "site2=site1=site3>site4=site5"),
  bain(lm_sample3, "site2&site3>site1&site4&site5")
)

@@

```
<!--The function returns an error stating that the samples have no hypothesis in common and thus the PBF cannot be calculated.-->

### Using sufficient statistics

A third use-case occurs when the raw data from different samples is not available.
This may happen, for example, when aggregating findings from the published literature (similar to meta-analysis).
In this case, one can use the default interface of `bain`, as explained in [REFERENCE BAIN PAPER Hoijtink, Mulder, van Lissa, & Gu, (2019) <doi:10.31234/osf.io/v3shc>].
This function requires four arguments: A named vector of parameter estimates, their asymptotic covariance matrix, the original sample size, and the number of within-group and between-group parameters.
These arguments may be derived in different ways for distinct samples.
The example below illustrates how to aggregate evidence in favor of one hypotheses across three studies that each used different methods.
<!-- CJ: What I'd like to do here is show how to aggregate a t-test, a regression coefficient and a correlation coefficient -->

```{r, eval = FALSE, echo = FALSE}
get_estimates <- function(sample){
  number_sites <- length(levels(sesamesim$site))

@@

And finally, on these objects, `pbf()` can be called.
```{r}
pbf(bain_allsamples_ests)
```
<!-- It is interesting that these estimates are not identical to the other examples... Is that because we do not have ALL information available in this use-case, or is something off in the script? -->
<!-- CJ: We should ask Herbert about this, but this example won't make it into this paper. If you want, you can send Herbert a reproducible example of the 'problem'!-->
